\section*{Preface}

\vspace{.5cm}

It is a great pleasure for us to host the 8th European Postgraduate Fluid Dynamics Conference (EPFDC) at the leading Warsaw universities: the Faculty of Physics, University of Warsaw (UW) and the Faculty of Power and Aeronautical Engineering, Warsaw University of Technology (WUT), our Alma Maters. 

This year edition is a part of Warsaw Fluid Dynamics Week 2016 (WFDW), which follows the tradition of weekly joined fluid dynamics related events at the University of Warsaw. It is preceeded by the EuHIT School on Turbulence (EST).

The 8th EPFDC gathers nearly 100 young researches from all over the world. Looking at the what is an extraordinary in comparison with the history of the previous EPFDC’s in participants number and variety of institution with every year. This year even representant of such countries as Australia, Brasil or Hong Kong decided that it is worth joining us in Warsaw despite of long distance to cover. 40 abstracts were selected for oral presentations and devided into 10 sessions. In additionone special session called ‘poster elevator pitch’ was planned as an innovative way ofgiving an opportunity to advertise in 2 min talk a poster before the poster session. 20 participants expressed their willingness to participate in this challenging but more and more popular and useful form of presentation. This is also the first time the conference takes palce at two different universities: the oral sessions at the UW and the poster session in the fluid dynamics labs of the WUT. To add a sense of healthy competition the participants were proposed to take part in the Outstanding Presentation Award contest. For this purpose a sponsor, Foundation Universitatis Varsoviensis, funded 4 scientific book vounchers for 3 outstanding oral presentations and 1 outstanding poster elevator pitch. The conference programme includes also 3 inspiring plenary lectures by experienced and successful academics: prof. Gregory Falkovich from Weizmann Institute of Science from Israel, prof. Piotr Smolarkiewicz from European Centre for Medium-Range Weather Forecasts (ECMWF) from the United Kingdom and prof. Piotr Szymczak from Faculty of Physics of University of Warsaw, who agreed to repleace prof. Hrvoje Jasak from Faculty of Mechanical Engineering and Naval Architecture, University of Zagreb from Croatia, who could not come to the conference due to personal reasons.

One of the main goal of EPFDC conferences is networking which we assure organizing besides the scientific program  two special social events. The first one will start on Wednesday afternoon and is a joined dinner of the WFDW, which plays a role of a welcome party for the 8th EPFDC and closing party for the EST. On Friday the beach party on the Vistula river bank was planned, which will be also an occasion to admire beautiful Warsaw Old Town landscape.

We hope that 8th EPFDC will be as inspiring, broadening horizons and boosting scientific networking among young researchers as previous editions. We wish all of you a fruitful and memorable experience.

Local Organizing Committee,\begin{itemize}
	\item Anna Górska 
\item Katarzyna Karpińska
\item Michal Remer 
\item Marcin Wyrozębski
\item Pawel Żuk
\end{itemize}

